---
title: "ishratc_OriginalHomeworkCode_05"
author: "Ishrat Chowdhury"
date: "November 6, 2019"
output: html_document
---

Problems I had:

1. When I am botostrapping, I get 1000 samples, but they are all the same numbers ina different order, asa result the model fot for each sample would be the same
2. I can only fit a linear regression model for samples one at a time, I cannot find a way to do all 1000 at once
3. I hit a wall here so I could not try getting the CI


First let's load in our data
```{r}
library(curl)
library(ggplot2)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, stringsAsFactors = FALSE)
attach(d)
head(d)
```

Run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean).

```{r}
d$logHomeRange <- log(d$HomeRange_km2)
d$logFemaleBodyMass <- log(d$Body_mass_female_mean)
m<-lm(data=d, logHomeRange ~ logFemaleBodyMass)
m
m$coefficients #lets see the coefficeints 
#the intercept (B0) is -9.44 and the slope (B1) is 1.04
```

Now let's use bootstrapping to sample our data 1000 times. I first want to make a new data frme with just the 2 variables so it is easier to deal with.

```{r}
d2<-data.frame(d$logHomeRange, d$logFemaleBodyMass)
d2
```

```{r}
k <- 1000 # number of samples
n <-  2 # size of each sample
s <- NULL # dummy variable to hold each sample
for (i in 2:k){
    s[[i]] <- sample(d2,size=n, replace=FALSE)
}
head(s)
summary(s)
```


```{r}
m2<-lm(data=s[[2]], d.logHomeRange ~ d.logFemaleBodyMass)
m2
m2$coefficients
```

this finds the lm for one sample, not sure how to make it do it for all of them, also the numbers are going to be the same. 

